\chapter{Bibliografía}

\hangindent=5em
\hangafter=-2

Ben-Kaabia, M., \& Gil Roig, J. M. (2008). Asimetrías en la transmisión de precios en el sector del tomate en España. Economía Agraria y Recursos Naturales, 8(1), 57-82.

Box, G. E., Jenkins, G. M., Reinsel, G. C., \& Ljung, G. M. (2015). Time series analysis: forecasting and control. John Wiley \& Sons.

Dickey, D. A., \& Fuller, W. A. (1979). Distribution of the estimators for autoregressive time series with a unit root. Journal of the American statistical association, 74(366a), 427-431.

Dickey, D. A., \& Fuller, W. A. (1981). Likelihood ratio statistics for autoregressive time series with a unit root. Econometrica: Journal of the Econometric Society, 1057-1072.

Di Narzo, A. F., Aznarte, J. L., \& Stigler, M. (2009). tsDyn: Time series analysis based on dynamical systems theory. R package version 0.7.(URL: \texttt{http://stat. ethz. ch/CRAN/web/packages/tsDyn/vignettes/tsDyn.pdf}.

Durbin, J., \& Koopman, S. J. (2012). Time series analysis by state space methods (Vol. 38). OUP Oxford.

Phillips, P. C., \& Perron, P. (1988). Testing for a unit root in time series regression. Biometrika, 75(2), 335-346.

Hansen, B. E., \& Seo, B. (2002). Testing for two-regime threshold cointegration in vector error-correction models. Journal of econometrics, 110(2), 293-318.

Hyndman, R. J., \& Khandakar, Y. (2007). Automatic time series for forecasting: the forecast package for R (No. 6/07). Monash University, Department of Econometrics and Business Statistics.

Koop, G., Pesaran, M. H., \& Potter, S. M. (1996). Impulse response analysis in nonlinear multivariate models. Journal of econometrics, 74(1), 119-147.

Johansen, S., Danielsdottir, A. K., Kristinsson, K., Petersen, P. H., \& Naevdal, G. (1996). Likelihood-Based Inference in Cointegrated Vector Autoregressive Models. Oxford University Press

Juselius, K. (2006). The cointegrated VAR model: methodology and applications. Oxford university press.

Kreiss, J. P., \& Lahiri, S. N. (2012). Bootstrap methods for time series. In Handbook of statistics (Vol. 30, pp. 3-26). Elsevier.

Lo, M. C., \& Zivot, E. (2001). Threshold cointegration and nonlinear adjustment to the law of one price. Macroeconomic Dynamics, 5(4), 533-576.

Lütkepohl, H. (2005). New introduction to multiple time series analysis. Springer Science \& Business Media.

Meyer, J., \& Cramon-Taubadel, S. (2004). Asymmetric price transmission: a survey. Journal of agricultural economics, 55(3), 581-611.

 Pfaff, B. (2008). VAR, SVAR and SVEC models: Implementation within R package vars. Journal of Statistical Software, 27(4), 1-32.

Tiffin, R., \& Dawson, P. J. (2000). Structural breaks, cointegration and the farm-retail price spread for lamb. Applied economics, 32(10), 1281-1286.

R Core Team (2017). R: A language and environment for statistical computing.
  R Foundation for Statistical Computing, Vienna, Austria. URL
  \texttt{https://www.R-project.org/}.

  